---
title: "Supplementary Data SD6"
author: ""
date: ""
output: pdf_document
header-includes: 
  - \usepackage{pdfpages}
---

```{r, setup, message = F, echo = F}
easypackages::packages("tidyverse")
```

This supplementary data file contains the diagnostic plots for our MCMCglmm mixed effects models. Models diagnostics were assessed using traceplots and Geweke plots to assess autocorrelation and convergence. All models demonstrated adequate convergence and minimal autocorrelation.

\
\

# Models
Below are the code chunks for our models. "overPCA" refers to overstory complexity values, "underPCA" refers to understory complexity values, "VAAN_CN_s" refers to lowbush blueberry carbon:nitrogen values, "VAAN_CP_s" refers to lowbush blueberry carbon:phosphorus values, sex refers to the sex of each individual, and CollarID refers to the individual's unique collar frequency. In total, 5 models were evaluated. We evaluated a global model, a stoichiometry model, a predation model, a sex model, and a null/intercept model.  
\
```{r, eval = F, echo = T}
global <- MCMCglmm(kUD ~ overPCA_s + underPCA_s + VAAN_CN_s + VAAN_CP_s + 
                     overPCA_s*VAAN_CN_s + overPCA_s*VAAN_CP_s + underPCA_s*VAAN_CN_s + 
                     underPCA_s*VAAN_CP_s + Sex, 
                   random =~ us(1 + underPCA_s):CollarID + us(1 + VAAN_CN_s):CollarID + 
                     us(1 + overPCA_s):CollarID + us(1 + VAAN_CP_s):CollarID, 
                   #family = "gaussian",
                   prior = prior0,
                   nitt=420000,
                   burnin=20000,
                   thin=100,
                   verbose = TRUE,
                   data = full_stack_s2,
                   pr=T, saveX = TRUE,saveZ = TRUE)

stoich <- MCMCglmm(kUD ~ VAAN_CN_s + VAAN_CP_s + VAAN_CN_s*VAAN_CP_s + Sex,
                   random =~ us(1 + VAAN_CN_s):CollarID + us(1 + VAAN_CP_s):CollarID, 
                   #family = "gaussian",
                   prior = prior1,
                   nitt=420000,
                   burnin=20000,
                   thin=100,
                   verbose = TRUE,
                   data = full_stack_s2,
                   pr=T, saveX = TRUE,saveZ = TRUE)

pred <- MCMCglmm(kUD ~ overPCA_s + underPCA_s + overPCA_s*underPCA_s + Sex, 
                 random =~ us(1 + underPCA_s):CollarID + us(1 + overPCA_s):CollarID, 
                   #family = "gaussian",
                   prior = prior2,
                   nitt=420000,
                   burnin=20000,
                   thin=100,
                   verbose = TRUE,
                   data = full_stack_s2,
                   pr=T, saveX = TRUE,saveZ = TRUE)

sex <- MCMCglmm(kUD ~ Sex,
                 random = ~CollarID,
                 #family = "gaussian",
                 prior = prior3,
                 nitt=420000,
                 burnin=20000,
                 thin=100,
                 verbose = TRUE,
                 data = full_stack_s2,
                 pr=T, saveX = TRUE,saveZ = TRUE)

intercept <- MCMCglmm(kUD ~ 1, 
                      random =~ CollarID, 
                      #family = "gaussian",
                      prior = prior3,
                      nitt=420000,
                      burnin=20000,
                      thin=100,
                      verbose = TRUE,
                      data = full_stack_s2,
                      pr=T, saveX = TRUE,saveZ = TRUE)
```

\newpage
# Model Diagnostics  
Below are the diagnostic plots, including traceplots and Geweke plots, for each of our models.

\
\

Figure SD6-1a. Traceplots for our global model.
```{r, echo = F, fig.align="center"}
knitr::include_graphics("/home/icrichmond/Repositories/kernels/graphics/traceplots_global.pdf")
```
\includepdf[pages={2-},pagecommand={}]{/home/icrichmond/Repositories/kernels/graphics/traceplots_global.pdf}

\newpage
Figure SD6-1b. Geweke plots for our global model.
```{r, echo = F, fig.align="center"}
knitr::include_graphics("/home/icrichmond/Repositories/kernels/graphics/gewekeplots_global.pdf")
```
\includepdf[pages={2-},pagecommand={}]{/home/icrichmond/Repositories/kernels/graphics/gewekeplots_global.pdf}




\newpage
Figure SD6-2a. Traceplots for our stoichiometry model.
```{r, echo = F, fig.align="center"}
knitr::include_graphics("/home/icrichmond/Repositories/kernels/graphics/traceplots_stoich.pdf")
```
\includepdf[pages={2-},pagecommand={}]{/home/icrichmond/Repositories/kernels/graphics/traceplots_stoich.pdf}

\newpage
Figure SD6-2b. Geweke plots for our stoichiometry model.
```{r, echo = F, fig.align="center"}
knitr::include_graphics("/home/icrichmond/Repositories/kernels/graphics/gewekeplots_stoich.pdf")
```
\includepdf[pages={2-},pagecommand={}]{/home/icrichmond/Repositories/kernels/graphics/gewekeplots_stoich.pdf}




\newpage
Figure SD6-3a. Traceplots for our perceived predation risk model.
```{r, echo = F, fig.align="center"}
knitr::include_graphics("/home/icrichmond/Repositories/kernels/graphics/traceplots_pred.pdf")
```
\includepdf[pages={2-},pagecommand={}]{/home/icrichmond/Repositories/kernels/graphics/traceplots_pred.pdf}

\newpage
Figure SD6-3b. Geweke plots for our perceived predation risk model.
```{r, echo = F, fig.align="center"}
knitr::include_graphics("/home/icrichmond/Repositories/kernels/graphics/gewekeplots_pred.pdf")
```
\includepdf[pages={2-},pagecommand={}]{/home/icrichmond/Repositories/kernels/graphics/gewekeplots_pred.pdf}




\newpage
Figure SD6-4a. Traceplots for our sex model.
```{r, echo = F, fig.align="center"}
knitr::include_graphics("/home/icrichmond/Repositories/kernels/graphics/traceplots_sex.pdf")
```
\includepdf[pages={2-},pagecommand={}]{/home/icrichmond/Repositories/kernels/graphics/traceplots_sex.pdf}

\newpage
Figure SD6-4b. Geweke plots for our sex model.
```{r, echo = F, fig.align="center"}
knitr::include_graphics("/home/icrichmond/Repositories/kernels/graphics/gewekeplots_sex.pdf")
```
\includepdf[pages={2-},pagecommand={}]{/home/icrichmond/Repositories/kernels/graphics/gewekeplots_sex.pdf}




\newpage
Figure SD6-5a. Traceplots for our intercept model.
```{r, echo = F, fig.align="center"}
knitr::include_graphics("/home/icrichmond/Repositories/kernels/graphics/traceplots_intercept.pdf")
```
\includepdf[pages={2-},pagecommand={}]{/home/icrichmond/Repositories/kernels/graphics/traceplots_intercept.pdf}

\newpage
Figure SD6-5b. Geweke plots for our intercept model.
```{r, echo = F, fig.align="center"}
knitr::include_graphics("/home/icrichmond/Repositories/kernels/graphics/gewekeplots_intercept.pdf")
```
\includepdf[pages={2-},pagecommand={}]{/home/icrichmond/Repositories/kernels/graphics/gewekeplots_intercept.pdf}

