---
title: "Supplementary Data SD6"
author: ""
date: ""
output: pdf_document
header-includes:
  - \usepackage{pdfpages}
  - \usepackage{longtable}
---

This supplementary file contains the results of a power analysis as outlined in Martin *et al.* (2011, *Methods in Ecology & Evolution*). Please note that the power analysis is based on a frequentist models (see results below), and that the main analysis rather uses Bayesian generalized linear models. The data was found to have sufficient power for all random effects.  

# Model
Below outlines the code used for representing our global model. As this is the model that requires the most power, this is the one we evaluated using the power analysis. 
```{r, eval=F, echo=T}
global <- lmerTest::lmer(kUD ~ Overstory Complexity + Understory Complexity + 
                           Blueberry C:N + Blueberry C:P + 
                           Overstory Complexity * Blueberry C:N + 
                           Overstory Complexity * Blueberry C:P + 
                           Understory Cmplexity * Blueberry C:N + 
                           Understory Complexity * Blueberry C:P + 
                           (1 + Blueberry C:N | CollarID)  + 
                           (1 + Blueberry C:P | CollarID) + 
                           (1 + Overstory Complexity | CollarID) + 
                           (1 + Understory Complexity | CollarID),
                           data=dataset)
```

# Power Analysis 
Below is the code used to perform the power analysis on the various random effects found in our global model. We used the EAMM function from the ```pamm``` package.
```{r, eval = F, echo = T}
overstory_power <- EAMM(numsim = 10, mer.model = list(global, 
                                                      env = "Overstory Complexity",
                                                      random = "CollarID"))
understory_power <- EAMM(numsim = 10, mer.model = list(global, 
                                                       env = "Understory Complexity", 
                                                       random = "CollarID"))
CN_power <- EAMM(numsim = 10, mer.model = list(global, 
                                               env = "Blueberry C:N", 
                                               random = "CollarID"))
CP_power <- EAMM(numsim = 10, mer.model = list(global, 
                                               env = "Blueberry C:P", 
                                               random = "CollarID"))
```

\newpage
# Output
Below shows the output of the power analyses.   


Table 1. Power analysis output for the random slopes of overstory complexity and individual CollarID. CI low and high variance indicate the 95% confidence intervals for the variance in slope. CI low and high power indicate the 95% confidence intervals for the power of slope. Power indicates the estimated power level for each simulation (1 indicates sufficient power).
```{r, eval = T, echo = F, warning=F}
library("kableExtra", "dplyr", "tibble")
pa_g_over <- readRDS("large/powerOverstory.rds")

pa_g_over <- tibble::as_tibble(pa_g_over)

pa_g_over[c("VS", "sl.pval", "CIlow.slpv", "CIup.slpv", 
            "sl.power", "CIlow.slpo", "CIup.slpo")] %>%
  dplyr::mutate_if(is.numeric, format, digits=3) %>%
  kable(longtable = T, 
        col.names = c("Slope Variance", "p-value", "CI low variance", 
                      "CI high variance", "Power", "CI low power", 
                      "CI high power"))%>%
  row_spec(0,bold=TRUE)  %>%
  kable_styling(full_width = F, position="left", latex_options = ("repeat_header"))

```

\newpage
Table 2. Power analysis output for the random slopes of understory complexity and individual CollarID. CI low and high variance indicate the 95% confidence intervals for the variance in slope. CI low and high power indicate the 95% confidence intervals for the power of slope. Power indicates the estimated power level for each simulation (1 indicates sufficient power).
```{r, eval = T, echo = F}
library("kableExtra", "dplyr", "tibble")
pa_g_under <- readRDS("large/powerUnderstory.rds")

pa_g_under <- tibble::as_tibble(pa_g_under)

pa_g_under[c("VS", "sl.pval", "CIlow.slpv", "CIup.slpv", 
            "sl.power", "CIlow.slpo", "CIup.slpo")] %>%
  dplyr::mutate_if(is.numeric, format, digits=3) %>%
  kable(longtable = T, 
        col.names = c("Slope Variance", "p-value", "CI low variance", 
                      "CI high variance", "Power", "CI low power", 
                      "CI high power"))%>%
  row_spec(0,bold=TRUE)  %>%
  kable_styling(full_width =F, position="left", latex_options = ("repeat_header"))

```

\newpage
Table 3. Power analysis output for the random slopes of lowbush blueberry carbon:nitrogen (C:N) and individual CollarID. CI low and high variance indicate the 95% confidence intervals for the variance in slope. CI low and high power indicate the 95% confidence intervals for the power of slope. Power indicates the estimated power level for each simulation (1 indicates sufficient power).
```{r, eval = T, echo = F}
library("kableExtra", "dplyr", "tibble")
pa_g_cn <- readRDS("large/powerCN.rds")

pa_g_cn <- tibble::as_tibble(pa_g_cn)

pa_g_cn[c("VS", "sl.pval", "CIlow.slpv", "CIup.slpv", 
            "sl.power", "CIlow.slpo", "CIup.slpo")] %>%
  dplyr::mutate_if(is.numeric, format, digits=3) %>%
  kable(longtable = T, 
        col.names = c("Slope Variance", "p-value", "CI low variance", 
                      "CI high variance", "Power", "CI low power", 
                      "CI high power"))%>%
  row_spec(0,bold=TRUE)  %>%
  kable_styling(full_width=F,position="left", latex_options = ("repeat_header"))

```

\newpage
Table 4. Power analysis output for the random slopes of lowbush blueberry carbon:phosphorus (C:P) and individual CollarID. CI low and high variance indicate the 95% confidence intervals for the variance in slope. CI low and high power indicate the 95% confidence intervals for the power of slope. Power indicates the estimated power level for each simulation (1 indicates sufficient power).
```{r, eval = T, echo = F}
library("kableExtra", "dplyr", "tibble")
pa_g_cp <- readRDS("large/powerCP.rds")

pa_g_cp <- tibble::as_tibble(pa_g_cp)

pa_g_cp[c("VS", "sl.pval", "CIlow.slpv", "CIup.slpv", 
            "sl.power", "CIlow.slpo", "CIup.slpo")] %>%
  dplyr::mutate_if(is.numeric, format, digits=3) %>%
  kable(longtable = T, 
        col.names = c("Slope Variance", "p-value", "CI low variance", 
                      "CI high variance", "Power", "CI low power", 
                      "CI high power"))%>%
  row_spec(0,bold=TRUE)  %>%
  kable_styling(full_width = F, position="left", latex_options = ("repeat_header"))

```